\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}


\begin{center}
    \textbf{\Huge \scshape Ayub Farah} \\ \vspace{1pt}
    \small (346)-622-1183 $|$ \href{mailto:ayubaf04@gmail.com}{\underline{ayubaf04@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ayubfarah}{\underline{linkedin.com/in/ayubfarah}} $|$
    \href{https://ayubfarah.com}{\underline{ayubfarah.com}} $|$
    \href{https://github.com/ayubf}{\underline{github.com/ayubf}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{Houston, TX}
      {Bachelor of Science in Mathematics, Computer Science}{(Expected) May 2026} 
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cisco Meraki}
      {May 2025 -- August 2025}
      {Software Engineering Intern}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Built a frontend interface for filtering and searching firewall rules in the Cisco Meraki Dashboard using \textbf{TypeScript} and \textbf{Redux}.}
        \resumeItem{Implemented backend API routes in \textbf{Ruby on Rails} to support advanced rule filtering and search queries.}
        \resumeItem{Integrated \textbf{OpenAI ChatGPT API} to enable natural language-driven rule searches, allowing users to auto-generate and populate form fields from plain-text descriptions.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Web Services}
      {May 2024 -- August 2024}
      {Software Development Engineering Intern}{Santa Clara, CA}
      \resumeItemListStart
        \resumeItem{Streamlined user membership deletion management as part of the latest release of AWS Clean Rooms ML.}
        \resumeItem{Created \textbf{AWS Lambda} handlers, tests, modules, and proxies (with \textbf{Dagger}) in \textbf{Kotlin}. }
        \resumeItem{Designed and deployed cloud infrastructure with AWS CDK in TypeScript, and wrote unit and integration tests.}
        \resumeItem{Integerated resources across teams using a relay built with \textbf{AWS DDB Streams, AWS SQS} and 
        \textbf{AWS SNS}.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Web Services}{June 2023 -- August 2023}
      {Software Development Engineering Intern}{Santa Clara, CA}
      \resumeItemListStart
        \resumeItem{Developed a resource metadata viewer application utilizing \textbf{AWS Lambda} \&\ \textbf{DynamoDB}, enhancing accessibility and efficiency for the engineering team's resource management.}
        \resumeItem{Implemented role-based access control using \textbf{AWS IAM}, ensuring secure and streamlined access for team members within the resource metadata viewer application.}
        \resumeItem{Enhanced the team's ticket management application with \textbf{React} and \textbf{Python}, integrating crucial edit functionalities to streamline the ticketing process and improve team productivity.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

  \section{Professional Development}

  \resumeSubHeadingListStart

    \resumeSubheading
    {Google}{July 2022 - August 2022}
    {Computer Science Summer Institute (CSSI) Scholar}{Remote}
    \resumeItemListStart
        \resumeItem{Participated in a 4-week intensive computer science summer program for high-achieving students.}
        \resumeItem{Completed an introductory project-based HTML/CSS and JavaScript curriculum taught by Google engineers.}
        \resumeItem{Attended product design, resume development, and software engineering interview workshops.}
        \resumeItem{Delivered a collaborative final project presentation that included a live demonstration to Google employees and community leaders.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Turms} $|$ \emph{WebSocket API, Go, React, JWT. MongoDB, TypeScript}}{}
          \resumeItemListStart
            \resumeItem{Created a real-time messaging app using the \textbf{WebSocket API}.}
            \resumeItem{Implemented secure user session management with encrypted \textbf{JWTs} for heightened privacy.}
            \resumeItem{Created a dynamic chat room system with automated lifecycle management using \textbf{Go} and \textbf{MongoDB}.}
            \resumeItem{Designed a dynamic and responsive frontend using \textbf{TypeScript} and \textbf{React}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, TypeScript, Ruby, Kotlin, Go, PostgreSQL, R} \\
     \textbf{Frameworks}{: React, Node.js, Flask, Express, Ruby on Rails, Redux} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Dagger, JUnit, Jest, Rspec}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}